Technical Report

### 2017-11-03 fully-abstract-comp/technical-report.tex
typos and minor omissions.

  \tsem{\tsplit{r_1}{r_2}{r_3}{r_4}} = &

@@

\[
  \comp{\scall{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \iota_A \defeq (*,=,=,H_A)
\]
where $H_A$ is defined as follows:
\[
  H_A \; s \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(\xi(\hat{W}))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}

>>>>

  \sem{\tsplit{r_1}{r_2}{r_3}{r_4}} = &

@@

\[
  \comp{\scall{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \iota_A \defeq (\normal,*,=,=,H_A)
\]
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A \; s \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(\xi(\hat{W}))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}
